---
title: "1. Exploratory Data Analysis"
output: html_notebook
---

```{r}
load.libraries <- c('data.table', 'testthat', 'gridExtra', 'corrplot', 'GGally', 'ggplot2', 'e1071', 'dplyr','plyr')
install.lib <- load.libraries[!load.libraries %in% installed.packages()]
for(libs in install.lib) install.packages(libs, dependences = TRUE)
sapply(load.libraries, require, character = TRUE)
```

### Data Source

We will try to use data from 2 sources:

* From Lahman's Database for statistics https://github.com/chadwickbureau/baseballdatabank 
* From Retrosheet for game logs and boxscores at https://www.retrosheet.org/site.htm

___
__Copyright Notice:__ 

_The Databank is historically based in part on the Lahman Baseball Database, 
version 2015-01-24, which is Copyright (C) 1996-2015 by Sean Lahman._

_This information is available free of charge from and is copyrighted
by Retrosheet.  Interested parties may contact Retrosheet at 
http://www.retrosheet.org. _


### Teams Data


```{r}
Teams <- fread("./data_raw/core/Teams.csv")
Teams %>% dim()
```

Ok there seems to be weird, since there is only 15 teams in NL and 15 teams in AL




```{r}
Teams %>% head()
```

```{r}
Teams %>% tail()
```


Ok, we can see that this is simpy the historical data from 1871 of all the teams performance in all historical season up to 2017


Let's take a look at available features for 
```{r}
Teams %>% colnames()
```

Now we wil separate those features into categorical, numerical 
```{r}
teams_categorical_feat <- names(Teams)[which(sapply(Teams, is.character))]
teams_numerical_feat <- names(Teams)[which(sapply(Teams, is.numeric))]
```

```{r}
teams_categorical_feat
```

```{r}
teams_numerical_feat
```

__Feature abbreviation meaning:__

* "HR": Home Run
* "SHO": Shutout: A starting pitcher is credited with a shutout when he pitches the entire game for a team and does not allow the opposition to score. By definition, any pitcher who throws a shutout is also awarded a win. Because he recorded every out for his team and didn't allow a run, his team could only have won.
* "BPF":
* "Rank":
* "BB":
* "SV": 
* "PPF":
* "G": Number of games played per season
* "SO" : Strikeouts
* "IPouts":
* "Ghome":
* "SB":
* "HA":
* "W":
* "CS":
* "HRA":
* "L":
* "HBP":
* "BBA":
* "R":
* "SF":
* "SOA":
* "AB":
* "RA":
* "E":
* "H":
* "ER":
* "DP":
* "2B": Double : A batter is credited with a double when he hits the ball into play and reaches second base without the help of an intervening error or attempt to put out another baserunner.
* "ERA": Earned Run Average : Earned run average represents the number of earned runs a pitcher allows per nine innings -- with earned runs being any runs that scored without the aid of an error or a passed ball. ERA is the most commonly accepted statistical tool for evaluating pitchers.
* "FP":
* "3B":
* "CG":
* "attendance":


### Batting

```{r}
Batting <- fread("data_raw/core/Batting.csv")
Batting %>% dim()
```
```{r}
Batting %>% tail()
```

```{r}
Batting %>% colnames()
```

__Features:__

* "G": Games
* "AB": 
* "R": 
* "H": 
* "2B": 
* "3B": 
* "HR": 
* "RBI": 
* "SB": 
* "CS": 
* "BB": 
* "SO": 
* "IBB": 
* "HBP": 
* "SH": 
* "SF": 
* "GIDP": 



